\problemname{Closeness Queries}
In an undirected graph, we define the distance between two vertices $u$ and $v$ as the minimum length of a sequence of edges starting at $u$ and ending at $v$.
Given $Q$ pairs of vertices in the graph, can you for each pair of vertices compute the distance between them?

The $M$ edges of the graph have been chosen using the following method:
\begin{verbatim}
for i between 1...M:
    choose a random edge not in the graph
    add the edge to the graph
\end{verbatim}

The $Q$ queries have been chosen using the following method:
\begin{verbatim}
for i between 1...Q:
    choose a random pair of distinct vertices
\end{verbatim}

\section*{Input}
The first line contains the integers $N$ and $M$ ($N = 45\,000$, $M = 200\,000$). 

The next $M$ lines contains the edges of the graph.
Each line consists of two integers $u$ and $v$ ($0 \le u \neq v < N$, the vertices of the edge).

This is followed by a line containing the number of pairs of vertices $Q$ ($1 \le Q \le 10\,000$).

The next and final $Q$ lines each contains two \textbf{distinct} integers: the name of the vertices in a pair.

\section*{Output}
For each pair of vertices in the input, output the distance between them.

If there is no path between the vertices, output \texttt{-1}.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points.
To get the points for a test group you need to solve all test cases in the test group.

\textbf{Note}: For group $2$, you can get part of the score.
Let the correct distance for a pair be $d$ and your answer be $d'$.
If $d' \le d \le 2d'$ for every query or no path exists (and you give an arbitrary integer answer between $-1$ and $N$), you will receive $15$ points. 

\noindent
\begin{tabular}{| l | l | p{10cm} |}
  \hline
    \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $10$        &  $Q = 1$ \\ \hline
  $2$    & $30$       & No additional constraints. \\ \hline
\end{tabular}
