\problemname{Evasion}
A monster is chasing you in a tree with $N$ vertices, labeled between $1$ and $N$.
Initially, the monster starts at vertex $1$ and you start at vertex $2$.
Through careful analysis of the monster's hunting patterns you have concluded that it will move to the (not necessarily distinct) $M$ vertices $a_1$, $a_2$, $\dots$, $a_M$ in order, where $a_i$ and $a_{i+1}$ are adjacent in the tree for all $1 \le i \le M - 1$.

You are trying to keep away from the monster, while performing as few moves as possible.
A move means moving from a vertex to an adjacent vertex.
Before each of the monster's moves, you may make any number of moves.

What is the minimal number of moves you have to make?

\section*{Input}
The first line contains the integers $N$ ($2 \le N \le 100\,000$) and $M$ ($1 \le M \le 500\,000$), the number of vertices in the tree and the number of moves the monster performs.

The next $N-1$ lines contains the edges of the tree.
Each line consists of two integers $u$ and $v$ ($1 \le u \neq v \le N$), the vertices of the edge.

The final line contains the $M$ numbers $a_1, \dots, a_M$, the vertices the monster moves through ($1 \le a_i \le N$) in order.
It is guaranteed that $a_i$ and $a_{i+1}$ are adjacent vertices of the tree for $1 \le i \le M-1$, and that vertices $1$ and $a_1$ are adjacent.

\section*{Output}
Output a single integer, the minimal number of moves you have to perform to avoid the monster.

If avoiding the monster is impossible, output \texttt{-1}.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points.
To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{10cm} |}
  \hline
  Group & Points & Constraints \\ \hline
  $1$   & $23$   & $N \le 100$, $M \le 500$ \\ \hline
  $2$   & $27$   & Each vertex has degree at most $3$. \\ \hline
  $3$   & $50$   & No additional constraints. \\ \hline
\end{tabular}
